nuclear energy in comparison

### 2024-01-24 corstuff.Rmd
the problem of correlation

@@

# 3 linear models - 1) lm with demographic variables except age and State
TM_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = TM)

@@

>>>>

fascales_mice <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))%>%
  na.omit()

@@

TMalldemos <- joineddf %>%
            filter(State =="Tamil Nadu")%>%
            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State)

# 3 linear models - 1) lm with demographic variables except age and State
TM_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +age, data = TMalldemos)

summary(TM_demo)

@@

TM2<- fascale_scores2 %>%
  filter(State == "Tamil Nadu")

# 3) lm with kahan 
TM2_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + Communitarianism_score + Egalitarianism_score, data = TM2)

summary(TM2_kahan)

# 4) lm with ecopolvars 
TM2_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + Communitarianism_score + Egalitarianism_score , data = TM2)

summary(TM2_allscales)

TM2_ecopol <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age +  Pdevelop + Ndevelop,  data = TM2)

summary(TM2_ecopol)

### 2024-01-24 nuclear in comparison.Rmd
the problem of correlation

@@

## Net benefit by state

>>>>

str(data_by_state)
str(joineddf)

@@

# Maharshtra t tests

```{r, echo = FALSE, fig.width=14, fig.height=6}

Mperceivedrisk <- joineddf %>% 
  filter(State == "Maharashtra")%>%
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttestM <- pairwise.t.test(Mperceivedrisk$perceived_risk, Mperceivedrisk$technology, p.adjust.method = "BH")

tidy_result_ttestM <- broom::tidy(result_ttestM)

Mheatmap1 <- ggplot(tidy_result_ttestM, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

Mperceivedbenefit <-joineddf %>% 
  filter(State=="Maharashtra")%>%
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestbenM <- pairwise.t.test(Mperceivedbenefit$perceived_benefit, Mperceivedbenefit$technology, p.adjust.method = "BH")

tidy_resultbcM <- broom::tidy(result_ttestbenM)

library(ggplot2)
Mheatmap2 <- ggplot(tidy_resultbcM, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(Mheatmap1, Mheatmap2, ncol=2)

# Tamil Nadu  t tests

```{r, echo = FALSE, fig.width=14, fig.height=6}

TMperceivedrisk <- joineddf %>% 
  filter(State == "Tamil Nadu")%>%
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttestTM <- pairwise.t.test(TMperceivedrisk$perceived_risk, TMperceivedrisk$technology, p.adjust.method = "BH")

tidy_result_ttestTM <- broom::tidy(result_ttestTM)

TMheatmap1 <- ggplot(tidy_result_ttestTM, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

TMperceivedbenefit <-joineddf %>% 
  filter(State=="Tamil Nadu")%>%
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestbenTM <- pairwise.t.test(TMperceivedbenefit$perceived_benefit, TMperceivedbenefit$technology, p.adjust.method = "BH")

tidy_resultbcTM <- broom::tidy(result_ttestbenTM)

library(ggplot2)
TMheatmap2 <- ggplot(tidy_resultbcTM, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(TMheatmap1, TMheatmap2, ncol=2)

# Uttar Pradesh  t tests

```{r, echo = FALSE, fig.width=14, fig.height=6}

UPperceivedrisk <- joineddf %>% 
  filter(State == "Uttar Pradesh")%>%
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttestUP <- pairwise.t.test(UPperceivedrisk$perceived_risk, UPperceivedrisk$technology, p.adjust.method = "BH")

tidy_result_ttestUP <- broom::tidy(result_ttestTM)

UPheatmap1 <- ggplot(tidy_result_ttestUP, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

UPperceivedbenefit <-joineddf %>% 
  filter(State=="Uttar Pradesh")%>%
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestbenUP <- pairwise.t.test(UPperceivedbenefit$perceived_benefit, UPperceivedbenefit$technology, p.adjust.method = "BH")

tidy_resultbcUP <- broom::tidy(result_ttestbenUP)

library(ggplot2)
UPheatmap2 <- ggplot(tidy_resultbcUP, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(UPheatmap1, UPheatmap2, ncol=2)

# Rajasthan  t tests

```{r, echo = FALSE, fig.width=14, fig.height=6}

Rperceivedrisk <- joineddf %>% 
  filter(State == "Rajasthan")%>%
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttestR <- pairwise.t.test(Rperceivedrisk$perceived_risk, Rperceivedrisk$technology, p.adjust.method = "BH")

tidy_result_ttestR <- broom::tidy(result_ttestR)

Rheatmap1 <- ggplot(tidy_result_ttestR, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

Rperceivedbenefit <-joineddf %>% 
  filter(State=="Rajasthan")%>%
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestbenR <- pairwise.t.test(Rperceivedbenefit$perceived_benefit, Rperceivedbenefit$technology, p.adjust.method = "BH")

tidy_resultbcR <- broom::tidy(result_ttestbenR)

library(ggplot2)
Rheatmap2 <- ggplot(tidy_resultbcR, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(Rheatmap1, Rheatmap2, ncol=2)

# West Bengal  t tests

```{r, echo = FALSE, fig.width=14, fig.height=6}

WBperceivedrisk <- joineddf %>% 
  filter(State == "West Bengal")%>%
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttestWB <- pairwise.t.test(WBperceivedrisk$perceived_risk, WBperceivedrisk$technology, p.adjust.method = "BH")

tidy_result_ttestWB <- broom::tidy(result_ttestWB)

WBheatmap1 <- ggplot(tidy_result_ttestWB, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

WBperceivedbenefit <-joineddf %>% 
  filter(State=="West Bengal")%>%
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestbenWB <- pairwise.t.test(WBperceivedbenefit$perceived_benefit, WBperceivedbenefit$technology, p.adjust.method = "BH")

tidy_resultbcWB <- broom::tidy(result_ttestbenWB)

library(ggplot2)
WBheatmap2 <- ggplot(tidy_resultbcWB, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(WBheatmap1, WBheatmap2, ncol=2)

```
## Net benefit by state
